---
title: "T12 Annotations"
author: "Julianna Renzi"
date: "2/7/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)
require(here)
```

This script processes the T12 annotations from RECHARGE, downloaded off CoralNet on Feb 7 2023

# Bring in the data

```{r}
# T12 annotations
annotations <- read_csv(here("data/annotations_T712_7Feb2023.csv"))

# we'll also bring in a key for dealing with many of the categories on coralnet (this is all from Tom's awesome code)
key <- read_csv(here("data/annotation_key.csv")) 

# and a metadata file for identifying plot treatments
trt_key <- read_csv(here("data/TRT_key.csv"))
```


# Clean up the data

Need to make the CoralNet file match the format of the csvs on the GoogleDrive

```{r}
annotations %>% 
  # this one also has some inconsistent labels for herbivory
  mutate(
    Herb_TRT = case_when(
      Herb_TRT == "1x1" ~ "1X1",
      Herb_TRT == "3x3" ~ "3X3",
      Herb_TRT == "open" ~ "Open",
      TRUE ~ Herb_TRT
    )
  ) %>% 
  select(-Date, -Row, -Column) %>% 
  # there's also a mistake for D3_Open_orthomosaic_T12 where the metadata was input incorrectly. Fix that here:
  mutate(Block = case_when(Name == "D3_Open_orthomosaic_T12.jpg" ~ "D",
                           TRUE ~ Block),
         Plot = case_when(Name == "D3_Open_orthomosaic_T12.jpg" ~ "3",
                           TRUE ~ Plot),
         Herb_TRT = case_when(Name == "D3_Open_orthomosaic_T12.jpg" ~ "Open",
                           TRUE ~ Herb_TRT)) %>% 
  mutate(Block_Plot = str_c(Block, Plot, sep = ""),
         Block_Plot_Herb_TRT = str_c(Block_Plot, Herb_TRT, sep = "_"),
         Count = 1) -> cover

```


Use the annotation key to get coarser taxa designations

```{r}
# first rename so colnames match
key %>% 
  mutate(Label = Taxa) -> key2

# then join key with RECHARGE data
cover %>% 
  left_join(key2, by = "Label") %>% 
  full_join(trt_key, by = "Block_Plot") -> recharge


```


Missing categories?

```{r}
recharge %>% 
  filter(is.na(Group.2)) %>% 
  select(Label) %>% unique() 
```



# Summarize at the plot level

```{r}
recharge %>% 
  group_by(Time_point, Block, Plot, Block_Plot, Herb_TRT, Group.2, Nutrient_Trt, Disturbance_Trt) %>% 
  # get count of each taxa per plot
  summarize(Count = sum(Count)) %>% 
  # pivot wider so each taxa gets a column
  pivot_wider(names_from = Group.2, values_from = Count) %>% 
  # replace NA values in the matrix with 0
  replace(is.na(.), 0) %>% 
  # get rid of points that are out
  select(-OUT)  %>% 
  ungroup() -> plots
  
```

# Get percent covers

```{r}

# first column we want
startcol <- grep("Acropora_spp", colnames(plots))

# last column we want
endcol <- grep("Lobophyla", colnames(plots))

# calculate the total cover
sum_cover <- cbind(plots, Plot_sum = rowSums(plots[, startcol:endcol]))

# and percent cover
perc_cover <- (sum_cover[,startcol:endcol]/sum_cover$Plot_sum) * 100

# then combine columns again for the full dataset
allDat <- cbind(plots[1:(startcol-1)], perc_cover) 
  
```


Make subsets for algal and coral cover based on Tom's code. First pick out macroalgal and coral columns

```{r}
# pick out algal columns
algalCols <- c(
  grep("Asparagopsis", colnames(allDat)),
  grep("Caulerpa_spp.", colnames(allDat)),
  grep("Dictyota_spp.", colnames(allDat)),
  grep("Foliose_Lobophora", colnames(allDat)),
  grep("Halimeda_spp.", colnames(allDat)),
  grep("Galaxaura_spp", colnames(allDat)),
  grep("Chlorodesmis_spp", colnames(allDat)),
  grep("Spatoglossum_spp", colnames(allDat)),
  grep("Padina", colnames(allDat)),
  grep("Red_articulated_calcified_algae", colnames(allDat)),
  grep("Sargassum", colnames(allDat)),
  grep("Turbinaria", colnames(allDat)),
  grep("Unknown_macroalgae", colnames(allDat)),
  grep("Valonia_spp.", colnames(allDat))
)


# pick out coral columns 
coralCols <- c(
  grep("Acanthastrea_spp", colnames(allDat)),
  grep("Acropora_spp", colnames(allDat)),
  grep("Fungiid", colnames(allDat)),
  grep("Leptastrea", colnames(allDat)),
  grep("Leptoseris", colnames(allDat)),
  grep("Lobophyla", colnames(allDat)),
  grep("Montipora_spp", colnames(allDat)),
  grep("Pavona", colnames(allDat)),
  grep("Phymastraea", colnames(allDat)),
  grep("Pocillopora_spp", colnames(allDat)),
  grep("Porites_spp", colnames(allDat)),
  grep("Psammocora", colnames(allDat)),
  grep("Unknown_encrusting_coral", colnames(allDat))
)
  
```

Then get those percent covers

```{r}
allDat$Macroalgae <- rowSums(allDat[ , algalCols])

allDat$Coral <- rowSums(allDat[ , coralCols])

```


# Save as CSV

```{r}
write_csv(allDat, here("generated_data/T12annotations.csv"))
```

