---
title: "Initial explore"
author: "Julianna Renzi"
date: "2/6/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


require(here)
require(tidyverse)
require(RColorBrewer)
```

This code does some initial exploration of the disease survey data collected by Julianna Renzi in the summer of 2022 in RECHARGE.

# Bring in the data

```{r}
surveys <- read_csv("data/disease_surveys.csv")
colony_counts <- read_csv("data/colony_counts_T12.csv")
```


# Explore Pavona EH

Get counts of EH colonies

```{r}
surveys %>% 
  filter(Genus == "Pavona" & Suspected_disease == "EH") %>% 
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt, Progression) %>% 
  summarize(Count = n()) %>% 
  pivot_wider(names_from = Progression, values_from = Count) %>% 
  full_join(colony_counts) %>%
  filter(Disturbance_Trt == "Intact") %>% 
  mutate(Medium = replace_na(Medium, 0),
         Mild = replace_na(Mild, 0),
         Severe = replace_na(Severe, 0)) %>% 
  ungroup() %>% 
  select(-Pocillopora_colonies, -Poc_norecruits, -Acropora_colonies, -Notes) %>% 
  pivot_longer(cols = c("Medium", "Mild", "Severe"),
               names_to = "Severity",
               values_to = "Count") %>% 
  # reorder factors
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  mutate(Severity = factor(Severity, levels = c("Mild", "Medium", "Severe"))) -> pavEH
```

## Plot

```{r}
pavEH %>% 
  ggplot(aes(x = Herbivory_trt, y = Count, fill = Severity)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt) +
  xlab("Herbivory treatment") +
  ylab("Number of Pavona colonies with EH")

ggsave(here("figs/PavEHAbundance.jpg"), height = 3.5, width = 6)
```

But, this doesn't mean anything! Because need to get colony counts 

# Pocillopora TL + Cil TL

```{r}
# what are our options here?
surveys %>% 
  filter(Genus == "Pocillopora") %>% 
  select(Suspected_disease) %>% unique() %>% arrange() %>% view()


```

Start with just the TL instances that seem the most sure?

```{r}

surveys %>% 
  filter(Genus == "Pocillopora" & (Suspected_disease == "TL_ciliate" | Suspected_disease == "TL")) %>% 
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt, Progression) %>% 
  summarize(Count = n()) %>% 
  pivot_wider(names_from = Progression, values_from = Count) %>% 
  full_join(colony_counts) %>%
  filter(Disturbance_Trt == "Intact") %>% 
  mutate(Acute = replace_na(Acute, 0),
         Subacute = replace_na(Subacute, 0),
         Chronic = replace_na(Chronic, 0)) %>% 
  ungroup() %>% 
  select(-Acropora_colonies, -Notes) %>% 
  pivot_longer(cols = c("Acute", "Subacute", "Chronic"),
               names_to = "Progression",
               values_to = "Count") %>% 
  # reorder factors
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  mutate(Progression = factor(Progression, levels = c("Chronic", "Subacute", "Acute"))) %>% 
  # get prevalences
  mutate(Prev_all = Count/Pocillopora_colonies,
         Prev_noRecruits = Count/Poc_norecruits) -> pocTL
  

```


## Plot

Just count (sloppy)

```{r}
pocTL %>% 
  ggplot(aes(x = Herbivory_trt, y = Count, fill = Progression, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)
```

All

```{r}
pocTL %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill = Progression, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)
```

No recruits

```{r}
pocTL %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_noRecruits, fill = Progression)) +
  geom_bar(stat = "identity", color = "gray") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)
```

The opposite way?

```{r}
pocTL %>% 
  ggplot(aes(x = Nutrient_Trt, y = Prev_all, color = Nutrient_Trt, fill = Progression)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Herbivory_trt)
```


### By progression

```{r}

pocTL %>% 
  filter(Progression == "Chronic") %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill =  Nutrient_Trt)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)

```

```{r}

pocTL %>% 
  filter(Progression == "Subacute") %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill =  Nutrient_Trt)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)

```

```{r}

pocTL %>% 
  filter(Progression == "Acute") %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill =  Nutrient_Trt)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)

```

Subacute + acute?

```{r}

pocTL %>% 
  filter(Progression == "Acute" | Progression == "Subacute") %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill = Progression, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)

```

## Model?

Make a df for all

```{r}
surveys %>% 
  filter(Genus == "Pocillopora" & (Suspected_disease == "TL_ciliate" | Suspected_disease == "TL")) %>% 
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt) %>% 
  summarize(Count = n()) %>% 
  full_join(colony_counts) %>%
  mutate(Count = replace_na(Count, 0)) %>%
  filter(Disturbance_Trt == "Intact") %>% 
  ungroup() %>% 
  select(-Acropora_colonies, -Notes) %>% 
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  # get prevalences
  mutate(Prev_all = Count/Pocillopora_colonies,
         Prev_noRecruits = Count/Poc_norecruits) -> pocTLmod
```

Make a model?

```{r}
mPoc <- glm(Count ~ Herbivory_trt + Nutrient_Trt + Herbivory_trt:Nutrient_Trt + offset(log(Pocillopora_colonies)), 
    family = poisson(link = "log"),
    data = pocTLmod)
  summary(mPoc) # stepwise selection just selects for nutrient enrichment
```




# Ciliate TL

Start with just the TL instances that seem the most sure?

```{r}
surveys %>% 
  filter(Genus == "Pocillopora" & (Suspected_disease == "TL_ciliate")) %>%
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt, Progression) %>% 
  summarize(Count = n()) %>% 
  pivot_wider(names_from = Progression, values_from = Count) %>% 
  full_join(colony_counts) %>%
  filter(Disturbance_Trt == "Intact") %>% 
  mutate(#Acute = replace_na(Acute, 0),
         Subacute = replace_na(Subacute, 0),
         Chronic = replace_na(Chronic, 0)) %>% 
  ungroup() %>% 
  select(-Acropora_colonies, -Notes) %>% 
  pivot_longer(cols = c( "Subacute", "Chronic"), 
               names_to = "Progression",
               values_to = "Count") %>% 
  # reorder factors
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  mutate(Progression = factor(Progression, levels = c("Chronic", "Subacute"))) %>% 
  # get prevalences
  mutate(Prev_all = Count/Pocillopora_colonies,
         Prev_noRecruits = Count/Poc_norecruits) -> pocTLcil
  

```


## Plot

Just count (sloppy)

```{r}
pocTLcil %>% 
  ggplot(aes(x = Herbivory_trt, y = Count, fill = Progression, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)
```

All

```{r}
pocTLcil %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill = Progression, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt) +
  xlab("Herbivory treatment") +
  ylab("Ciliate + tissue loss prevalence")


ggsave(here("figs/SEBprevalence.jpg"), height = 3.5, width = 6)


```

No recruits

```{r}
pocTLcil %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_noRecruits, fill = Progression)) +
  geom_bar(stat = "identity", color = "gray") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)
```

The opposite way?

```{r}
pocTLcil %>% 
  ggplot(aes(x = Nutrient_Trt, y = Prev_all, color = Nutrient_Trt, fill = Progression)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Herbivory_trt)
```


### By progression

```{r}

pocTLcil %>% 
  filter(Progression == "Chronic") %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill =  Nutrient_Trt)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)

```

```{r}

pocTLcil %>% 
  filter(Progression == "Subacute") %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill =  Nutrient_Trt)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)

```


Subacute + acute?

```{r}

pocTLcil %>% 
  filter(Progression == "Acute" | Progression == "Subacute") %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill = Progression, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)

```

## Model?

Make a df for all

```{r}
surveys %>% 
  filter(Genus == "Pocillopora" & (Suspected_disease == "TL_ciliate" )) %>% 
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt) %>% 
  summarize(Count = n()) %>% 
  full_join(colony_counts) %>%
  mutate(Count = replace_na(Count, 0)) %>% 
  filter(Disturbance_Trt == "Intact") %>% 
  ungroup() %>% 
  select(-Acropora_colonies, -Notes) %>% 
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  # get prevalences
  mutate(Prev_all = Count/Pocillopora_colonies,
         Prev_noRecruits = Count/Poc_norecruits) -> pocTLcilmod
```

Make a model?

```{r}
mPocCil <- glm(Count ~ Herbivory_trt + offset(log(Pocillopora_colonies)), 
    family = poisson(link = "log"),
    data = pocTLcilmod)
  summary(mPocCil) # a stepwise selects for herbivory treatment
```

# Poc "Bleaching"

Look at the "bleaching" instances. Remove chill ones for now?

```{r}
surveys %>% 
  filter(Genus == "Pocillopora" & (Suspected_disease == "Bleach_base_or_side")) %>%
  mutate(Progression = case_when(is.na(Progression) ~ "Normal", 
                                       TRUE ~ Progression)) %>% 
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt, Progression) %>% 
  summarize(Count = n()) %>% 
  pivot_wider(names_from = Progression, values_from = Count) %>% 
  full_join(colony_counts) %>%
  filter(Disturbance_Trt == "Intact") %>% 
  mutate(Normal = replace_na(Normal, 0),
         Chill = replace_na(Chill, 0)) %>% 
  ungroup() %>% 
  select(-Acropora_colonies, -Notes) %>% 
  pivot_longer(cols = c( "Normal", "Chill"), 
               names_to = "Severity",
               values_to = "Count") %>% 
  # reorder factors
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  mutate(Severity = factor(Severity, levels = c("Chill", "Normal"))) %>% 
  # get prevalences
  mutate(Prev_all = Count/Pocillopora_colonies,
         Prev_noRecruits = Count/Poc_norecruits) -> pocBleach
  

```


## Plot

Just count (sloppy)

```{r}
pocBleach %>% 
  ggplot(aes(x = Herbivory_trt, y = Count, fill = Severity, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)
```

All

```{r}
pocBleach %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill = Severity, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)
```

No recruits

```{r}
pocBleach %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_noRecruits, fill = Severity)) +
  geom_bar(stat = "identity", color = "gray") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)
```

The opposite way?

```{r}
pocBleach %>% 
  ggplot(aes(x = Nutrient_Trt, y = Prev_all, color = Nutrient_Trt, fill = Severity)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Herbivory_trt)
```


### By progression

```{r}

pocBleach %>% 
  filter(Severity == "Normal") %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill =  Nutrient_Trt)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt)

```


## Model

Make a df for all

```{r}
surveys %>% 
  filter(Genus == "Pocillopora" & (Suspected_disease == "Bleach_base_or_side" )) %>% 
  # remove chillers for now?
  filter(is.na(Progression)) %>% 
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt) %>% 
  summarize(Count = n()) %>% 
  full_join(colony_counts) %>%
  mutate(Count = replace_na(Count, 0)) %>% 
  filter(Disturbance_Trt == "Intact") %>% 
  ungroup() %>% 
  select(-Acropora_colonies, -Notes) %>% 
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  # get prevalences
  mutate(Prev_all = Count/Pocillopora_colonies,
         Prev_noRecruits = Count/Poc_norecruits) -> pocBleachmod
```

Make a model?

```{r}
mPocBleach <- glm(Count ~ Nutrient_Trt + Herbivory_trt + Nutrient_Trt:Herbivory_trt + offset(log(Pocillopora_colonies)), 
    family = poisson(link = "log"),
    data = pocBleachmod)
  summary(mPocBleach) # a stepwise function keeps interaction
```

# Bring in Lobophora percent cover

```{r}
annotations <- read_csv(here("generated_data/T12annotations.csv"))
```

## Join together with Poc TL

```{r}
# make annotation fields match
annotations %>% 
  rename(Herbivory_trt = Herb_TRT) -> annotations
 

pocTL %>% 
  # make join fields match
  rename(Block_Plot = Block) %>%  
  mutate(Herbivory_trt = as.character(Herbivory_trt)) %>% 
  mutate(Herbivory_trt = case_when(
      Herbivory_trt == "1x1" ~ "1X1",
      Herbivory_trt == "2x2" ~ "2X2",
      Herbivory_trt == "3x3" ~ "3X3",
      Herbivory_trt == "open" ~ "Open",
      TRUE ~ Herbivory_trt
  )) %>% 
  left_join(annotations) -> pocLoboph
```

## Real quick check Pavona cover

```{r}
pocLoboph %>% 
  ggplot(aes(x = Herbivory_trt, y = Pavona, fill = Nutrient_Trt)) +
  geom_boxplot() +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  xlab("Herbivory treatment") +
  ylab("Pavona (% cover)") +
  facet_wrap(~Nutrient_Trt) +
  theme(legend.position = "none")

ggsave(here("figs/PavPercentCov.jpg"), height = 3.5, width = 6)
```


## Plot TL vs. Loboph

Probably want to look at this vs. Macroalgae, Halimeda_spp, and Foliose_Lobophora

```{r}
pocLoboph %>% 
  ggplot(aes(x = Foliose_Lobophora, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() +
  facet_wrap(~Nutrient_Trt) # it would be hard to have less of a pattern here..
```

Macroalgae

```{r}
pocLoboph %>% 
  ggplot(aes(x = Macroalgae, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() +
  facet_wrap(~Nutrient_Trt) # it would be hard to have less of a pattern here..
```

Halimeda

```{r}
pocLoboph %>% 
  ggplot(aes(x = Halimeda_spp, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() +
  facet_wrap(~Nutrient_Trt) # it would be hard to have less of a pattern here..
```


## Join together with Poc TL ciliates

```{r}
pocTLcil %>% 
  # make join fields match
  rename(Block_Plot = Block) %>%  
  mutate(Herbivory_trt = as.character(Herbivory_trt)) %>% 
  mutate(Herbivory_trt = case_when(
      Herbivory_trt == "1x1" ~ "1X1",
      Herbivory_trt == "2x2" ~ "2X2",
      Herbivory_trt == "3x3" ~ "3X3",
      Herbivory_trt == "open" ~ "Open",
      TRUE ~ Herbivory_trt
  )) %>% 
  left_join(annotations) -> poccilLoboph
```

### Plot

```{r}
poccilLoboph %>% 
  ggplot(aes(x = Foliose_Lobophora, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() +
  facet_wrap(~Nutrient_Trt) # Again not much of a pattern--if anything negative
```

```{r}
poccilLoboph %>% 
  ggplot(aes(x = Macroalgae, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() +
  facet_wrap(~Herbivory_trt)  + # Again not much of a pattern--if anything negative
  xlab("Macroalgae % Cover") +
  ylab("Prevalence of ciliate TL") 

ggsave(here("figs/CiliateTLMacroalgae.jpg"), height = 3.5, width = 5)
```


## Join together with Poc Bleaching

```{r}
pocBleach %>% 
  # make join fields match
  rename(Block_Plot = Block) %>%  
  mutate(Herbivory_trt = as.character(Herbivory_trt)) %>% 
  mutate(Herbivory_trt = case_when(
      Herbivory_trt == "1x1" ~ "1X1",
      Herbivory_trt == "2x2" ~ "2X2",
      Herbivory_trt == "3x3" ~ "3X3",
      Herbivory_trt == "open" ~ "Open",
      TRUE ~ Herbivory_trt
  )) %>% 
  left_join(annotations) -> pocBleachLoboph
```

### Plot

```{r}
pocBleachLoboph %>% 
  ggplot(aes(x = Foliose_Lobophora, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() +
  facet_wrap(~Herbivory_trt) # noting 
```

```{r}
pocBleachLoboph %>% 
  ggplot(aes(x = Macroalgae, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() +
  facet_wrap(~Herbivory_trt) # noting 
```

```{r}
pocBleachLoboph %>% 
  ggplot(aes(x = Halimeda_spp, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() #+
  facet_wrap(~Herbivory_trt) # This looks the most positive of them all
```

# Acropora


```{r}
# what are our options here?
surveys %>% 
  filter(Genus == "Acropora") %>% 
  group_by(Suspected_disease) %>% summarize(N = n()) 


```

Start with just the TL instances that seem the most sure?

```{r}

surveys %>% 
  filter(Genus == "Acropora" & Suspected_disease == "TL") %>% 
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt, Progression) %>% 
  summarize(Count = n()) %>% 
  pivot_wider(names_from = Progression, values_from = Count) %>% 
  full_join(colony_counts) %>%
  filter(Disturbance_Trt == "Intact") %>% 
  mutate(Subacute = replace_na(Subacute, 0),
         Chronic = replace_na(Chronic, 0)) %>% 
  ungroup() %>% 
  select(-Pocillopora_colonies, -Poc_norecruits, -Notes) %>% 
  pivot_longer(cols = c("Subacute", "Chronic"),
               names_to = "Progression",
               values_to = "Count") %>% 
  # reorder factors
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  mutate(Progression = factor(Progression, levels = c("Chronic", "Subacute", "Acute"))) %>% 
  # get prevalences
  mutate(Prev_all = Count/Acropora_colonies) -> acropTL
  

```


## Plot

Just count (sloppy)

```{r}
acropTL %>% 
  ggplot(aes(x = Herbivory_trt, y = Count, fill = Progression, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt) 
```

All

```{r}
acropTL %>% 
  ggplot(aes(x = Herbivory_trt, y = Prev_all, fill = Progression, color = Nutrient_Trt,)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = brewer.pal(n = 3, name = "YlOrRd")) +
  theme_classic() + 
  facet_wrap(~Nutrient_Trt) +
  xlab("Herbivory treatment") +
  ylab("TL prevalence: Acropora") # BUT There are no Acropora in D2 3x3 and Open


ggsave(here("figs/AcroporaTLprevalence.jpg"), width = 6, height = 3.5)
```


## Model

Make a df for all

```{r}
surveys %>% 
  filter(Genus == "Acropora" & Suspected_disease == "TL") %>% 
  # start looking without thinking about size?
  group_by(Block, Herbivory_trt) %>% 
  summarize(Count = n()) %>% 
  full_join(colony_counts) %>%
  mutate(Count = replace_na(Count, 0)) %>% 
  filter(Disturbance_Trt == "Intact") %>% 
  ungroup() %>% 
  select(-Pocillopora_colonies, -Poc_norecruits, -Notes) %>% 
  mutate(Herbivory_trt = factor(Herbivory_trt, levels = c("1x1", "2x2", "3x3", "open"))) %>% 
  # get prevalences
  mutate(Prev_all = Count/Acropora_colonies) %>% 
  # remove infinite values
  filter(!is.nan(Prev_all)) -> acropTLmod
```

Make a model?

```{r}
mAcropTL <- glm(Count ~ Herbivory_trt + Nutrient_Trt + Herbivory_trt:Nutrient_Trt + offset(log(Acropora_colonies)), 
    family = poisson(link = "log"),
    data = acropTLmod)
  summary(mAcropTL) # stepwise selection just selects for nutrient enrichment but it doesn't look important..?
```

### Versus algae

```{r}
acropTL %>% 
  # make join fields match
  rename(Block_Plot = Block) %>%  
  mutate(Herbivory_trt = as.character(Herbivory_trt)) %>% 
  mutate(Herbivory_trt = case_when(
      Herbivory_trt == "1x1" ~ "1X1",
      Herbivory_trt == "2x2" ~ "2X2",
      Herbivory_trt == "3x3" ~ "3X3",
      Herbivory_trt == "open" ~ "Open",
      TRUE ~ Herbivory_trt
  )) %>% 
  left_join(annotations) -> acropTLLoboph
```

### Plot

```{r}
acropTLLoboph %>% 
  ggplot(aes(x = Foliose_Lobophora, y = Prev_all, color = Nutrient_Trt)) +
  geom_point() +
  theme_classic() +
  facet_wrap(~Herbivory_trt) # nothing--too few data points 
```


# How to deal with size? Mega df?

